---
title: "STAT805 Assignment 1"
subtitle: "Kexiang Huang"
output:
  word_document: default
  html_document:
    df_print: paged
  pdf_document: default
---

### Question 1: 

This is my function: 
\begin{equation}
\ f(x) = \sin(\sin(x^2)) + \cos(\frac{1}{1+x+x^2})-1
\end{equation}

> Task 1

Translate this function into R idiom and plot it for $x ∈ [−2, 2]$.
```{r}
x <- seq(from=-2, to=2, len=100)
f <- function(x){sin(sin(x^2)) + cos(1/(1+x+x^2))-1}
plot(x,f(x))
abline(0,0)
```

Let's verify the result.
```{r}
f(0) == (sin(sin(0)) + cos(1/(1+0+0))- 1)
```
<br><br/>

> Task 2

As we can see from the last graph, the function has 4 intersections with x-axis, they are seem like to be (-1.8,0), (-0.8,0), (0.5,0) and (1.8, 0) respectively. Thus we verify the area which is close to these intersections.

```{r}
uniroot(f,interval=c(-2,-1))
uniroot(f,interval=c(-1,-0))
uniroot(f,interval=c(0,1))
uniroot(f,interval=c(1,2))
```
The outputs are similar to our prediction. Subsequently, we verify it.
```{r}
plot(x,f(x),axes=FALSE,type='l') 
axis(1,pos=0) # x-axis, at (vertical) position 0
axis(2,pos=0) # y-axis, at (vertical) position 0
points(c(-1.745991,-0.8358447,0.4323219,1.768418),c(0,0,0,0),pch=4,cex=3,col='red')
```

Correct. All the points outputted through the function ```uniroot()``` sit on the x-axis as well as the intersections with the main function.
<br><br/>

> Task 3

The next stage is using definition method to differentiate the main function. 
\begin{equation}
\ f'(x) = \frac{f(x+\delta x)-f(x)}{\delta x}
\end{equation}
According to this clue, we can build an approximate derivative in the same range.
```{r}
dx <- 1e-6
fdash <- function(x){(f(x+dx)-f(x))/dx}
plot(x,fdash(x),main = "f'(x)")
abline(0,0)
```

Verifying it. All the maximum value and minimum value of the original function are fell in the position where the derivative function intersects at zero. It shows that $f'(x)$ is the correct derivative function of $f(x)$. 
```{r}
plot(x,f(x),type='l',main="f and fdash")
points(x,fdash(x),type='l',col='red')
legend("topleft",lty=1,col=c("black","red"),legend=c("f(x)","fdash(x)"))
abline(0,0)
```
<br><br/>

> Task 4

The minimum of this function in the domain $[-1,1]$ is below.
```{r}
optimize(f(x),c(-1,1))
```
Verifying it. It correctly marks the minimum value of function $f(x)$.
```{r}
plot(x,f(x))
points(c(-0.3038049),c(-0.6100053),pch=4,col="red",cex=4)
```
<br><br/>

> Task 5

Local maxima in the domain $[-2,2]$.
```{r}
optimize(f(x),c(-2,0),maximum = TRUE)
optimize(f(x),c(0,2),maximum = TRUE)
```
Verifying it. Both of them are the local maxima.
```{r}
plot(x,f(x))
points(c(-1.369005,1.270529),c(0.6032292,0.808012),pch=4,col="red",cex=4)
```
<br><br/>

> Task 6

The integration of this function from 0 to 2 can be described like this.
```{r}
z <- seq(from=0,to=2,len=100)
jj <- c(x,rev(x))
plot(x,f(x))
polygon(c(z,rev(z)),c(z*-1000000,f(rev(z))),col="red")
abline(v=0)
```

The value of this area equal 0.5021359:
```{r}
integrate(f,0,2)
```
Verifying. Calculate the sum of the areas under the function in the domain from 0 to 2.
```{r}
t <- seq(from=0, to=2,by=dx)
sum(f(t)*dx)
```

It is close to the output by function ```integrate()```, we can consider the function outcomes the correct result.

### Question 2:
This is my function:
\begin{equation}
\ f(x,y) = x^2 + y^2 + 7sin(x+y^2)
\end{equation}

> Task 1

Translate this function into R idiom and find the value of it when fulfil  $f(0.4,0.5)$.
```{r}
f <- function(x,y){x^2 + y^2 + 7*sin(x+y^2)}
f(0.4,0.5)
```
Verifying it through substitute the x=0.4 and y=0.5 into the above equation.
```{r}
f(0.4,0.5) == 0.4^2+0.5^2+7*sin(0.4+0.5^2)
```
<br><br/>

> Task 2

The contour graph of this function in the prescribed range would be like this.
```{r}
xvals <- seq(from = -3, to = +3, len=100)
yvals <- seq(from = -3, to = +3, len=100)
f <- function(v){
  x <- v[1]
  y <- v[2]
  return(x^2 + y^2 + 7*sin(x+y^2))
}
jj <- expand.grid(xvals,yvals)
 M <- apply(jj,1,f) 
 M <- matrix(M,100,100) 
 par(pty="s")
 contour(xvals,yvals,M,asp=1,xlim=range(xvals),ylim=range(yvals))
 persp(xvals,yvals,M) 
```
<br><br/>

> Task 3

Function ```optim()``` can be used to seek the local minimum of this function.
```{r}
optim(c(0.5,2),f)
```
Verifying it. It is indeed at the center of the contour.
```{r}
xvals <- seq(from = 0.5001312-0.1, to = 0.5001312+0.1,len=100)
yvals <- seq(from =2.0171683-0.1, to =2.0171683+0.1,len=100)
jj <- expand.grid(xvals,yvals)
M <- apply(jj,1,f) 
M <- matrix(M,100,100) 
par(pty="s")
contour(xvals,yvals,M,asp=1,xlim=range(xvals),ylim=range(yvals))
points(0.5001312,2.0171683,pch=16,col='red')
```
<br><br/>

> Task 4

Next stage is to explore the volume enclosed between the x-y plane and the function surface in the plotting region. It needs the package 'cubature', make sure you have download it ```install.packages("cubature")```before.  
```{r}
cubature::hcubature(f,rep(0,3),rep(1,3),tol=1e-4) 
```

### Question 3
This is my matrix:
$$
M=\left(\begin{array}{ccc} 
5 & 1 & 1\\
1 & 2 & 1\\
1 & 1 & 2
\end{array}\right)
$$

> Task 1

The method to calculate the det of this matrix is below.
```{r}
M <- matrix(c(5,1,1,1,2,1,1,1,2),3,3)
det(M)
```

Verifying it.
```{r}
det(M) == 5*2*2+1*1*1+1*1*1-1*2*1-1*1*2-1*1*5
```

And the trace of this matrix.
```{r}
tr <- function(A){sum(diag(A))}
tr(M)
```

Verifying it.
```{r}
trace <- function(A) {
  n <- dim(A)[1] 
  tr <- 0 
  for (k in 1:n) {
    l <- A[k,k]
    tr <- tr + l
  }
  return(tr[[1]])
}
tr(M) == trace(M)
```
<br><br/>

> Task 2

$M^{-1}$ can be found by:
```{r}
solve(M)
```

Verifying it, after multiply by the original matrix, each vector should be close to 0.
```{r}
solve(M) %*% M
```
<br><br/>

> Task 3

The eigenvectors and eigenvalues of this matrix is below.
```{r}
eigen(M)
```

According to the definition of eigenvalues $Ax=λx$, we can verify this result by this method.
```{r}
vec1 <- eigen(M)$vectors[,1]
val1 <- eigen(M)$values[1]
LHS <- M   %*% vec1           
RHS <- val1 *  vec1           
LHS <- c(LHS)                 
cbind(LHS,RHS, diff=LHS-RHS)
```

The 'diff' list showed the difference between matrix multiplication by A and scalar multiplication by λ, each value is close to 0, that means the equation is hold.
<br><br/>

> Task 4

The graph of $det (N(x))$ in the random (-3,4) would be like this.
```{r}
N <- function(x){
 matrix(c(5,1,x,1,2,1,x,1,2),3,3) 
}
Y <- function(M){
  det(M)
}
f <- function(x){Y(N(x))}
x <- seq(from=-3,to=4,len=100)
plot(x,sapply(x,f),type='l')
grid()
```

Then, we notice that:

* The determinant of 3*3 real symmetric matrix with 2 unknown variables in continuous range also satisfies symmetry.

* However, the axis of symmetry is not y=0 in this matrix.

* The property of its symmetry shows that The symmetric matrix can be diagonalized by some matrix.
<br><br/>

> Task 5

The eigenvalue of the instance matrix would be like this.
```{r}
#x <- seq(from=-1, to=1, len=20)
#y <- seq(from=-1, to=1, len=20)
#P <- function(v){
#  x <- v[1]
#  y <- v[2]
#  return(matrix(c(5,y,x,y,2,1,x,1,x),3,3))
#}
#P(x) - P(y) # Verify the relation about P(x,y)
#jj <- expand.grid(x,y)
#Z <- sapply(jj,P)
#eigen(Z)

eigen(matrix(c(5,-1,-1,-1,2,1,-1,1,-1),3,3)) # when x=-1, y=-1
eigen(matrix(c(5,-1,0,-1,2,1,0,1,0),3,3)) # when x=0, y=-1
eigen(matrix(c(5,-1,1,-1,2,1,1,1,1),3,3)) #when x=1, y=-1
eigen(matrix(c(5,0,-1,0,2,1,-1,1,-1),3,3)) #when x=-1, y=0
eigen(matrix(c(5,1,-1,1,2,1,-1,1,-1),3,3)) #when x=-1, y=1
eigen(matrix(c(5,0,0,0,2,1,0,1,0),3,3)) #when x=0, y=0
eigen(matrix(c(5,1,0,1,2,1,0,1,0),3,3)) #when x=0, y=1
eigen(matrix(c(5,0,1,0,2,1,1,1,1),3,3)) #when x=1, y=0
eigen(matrix(c(5,1,1,1,2,1,1,1,1),3,3)) #when x=1, y=1
```
Then we notice that:

* The eigenvalue when x=0, y=-1 is the same as the situation when x=0, y=1.

* However, the eigenvalue when x=-1, y=0 are not equal to x=1, y=0. 

* I predict that the eigenvalue when x=0, y=-n will be equal to the one when x=0, y=n in this instance. Conversely, it is invaild.

### Question 4
The processes of verifying are in the above.
<br>




<br/>



