---
title: "R Notebook"
output:
  word_document: default
  html_document:
    df_print: paged
---


load rdm
```{r}
rdm_ind = function(g1, g2, nreps){
  
  # g1: data before treatment
  # g2: data after treatment
   
  n1 = length(g1);
  n2 = length(g2);
  n  = n1+n2; # number of observations
  
  diffObt = mean(g2)- mean(g1);
  
  aux = c(g1, g2); # all observations
  
  out = numeric(nreps); # to store differences
  
  for(i in 1:nreps){
    
    d = sample(aux, size = n, replace = FALSE);
    
    out[i] = mean(d[(n1+1):n]) - mean(d[1:n1]);
    
  }
  
  highprob <- length(out[out >=  abs(diffObt)])/nreps;
  lowprob  <- length(out[out <= -abs(diffObt)])/nreps;
  prob2tailed <- lowprob + highprob;
  
  return(list(pvalue = prob2tailed, resampMeanDiff = out,
              diffObt = diffObt, nreps = nreps));
  
}
```

set up the data
```{r}
drug <- read.table("~/Downloads/abDrugEffect.dat",header = TRUE, check.names = TRUE)
x = cbind(drug[drug$treatment == "1", c("treatment","score1")], 
          drug[drug$treatment == "1",c("score2")])
colnames(x) = c("treatment","score1", "score2")
g1=drug[,4]; # Drug A score
g2=drug[,5]; # Drug B score
x=cbind(g1,g2)
```
print x
```{r}
x
```

load randomization for independent variables
```{r}
set.seed(1)
R = rdm_ind(g1, g2, nreps = 10000)
```
view r
```{r}
View(R)
```
hist
```{r}
pdf("drug.pdf")
dev.new()
hist(R$resampMeanDiff, xlab = "Mean difference", freq = F,
     main = "Distribution under Null hypothesis")
mtext("drugB - drugA", 3)
text(R$diffObt, 0.3, expression(paste("obs diff",sep="")))
arrows(R$diffObt, 75, R$diffObt, 0, length = .125);
text(4, 0.2, paste("p-value= ", R$pvalue ,sep=""))
```

95% CI
```{r}
n_psc  = length(g1);   # number of observations in drugA group
n_npsc = length(g2); # number of observations in drugB group

N = 1000; # number ofbootstrap samples
out = NULL; # number of bootstrap samples

for(i in 1:N){
  
  b_psc  = sample(1:n_psc, n_psc, replace = TRUE);
  b_npsc = sample(1:n_npsc, n_npsc, replace = TRUE);
  
  out = c(out, mean(g2[b_npsc]) - mean(g2[b_psc]));
  
}

dev.new()
hist(out,main = "Bootstrap sample",xlab ="p_hat");

round(quantile(out, probs = c(0.025,0.975)), 4);# 
```

covariate
```{r}
Ax=drug[drug$treatment == "1", "score1"];
Ay=drug[drug$treatment == "1", "score2"];
Bx=drug[drug$treatment == "2", "score1"];
By=drug[drug$treatment == "2", "score2"];

y = c(Ay,By) 
x = c(Ax,Bx)

n = length(y);

f = c(rep("A", length(Ax)), rep("B", length(Bx))); # factor
f = as.factor(f);

fit = lm(y ~ x + f); # linear model

plot(x,y); 
plot(fit);

summary(fit);

anova(fit);

### Randomization test ####

B   = 10000;
out = NULL;

set.seed(1)
for(i in 1:B){
  
  b     = sample(1:n, n, replace = FALSE);
  
  bfit  = lm(y[b] ~ x[b] + f);
  
  out   = c(out, summary(bfit)$coefficients[3,1]);
  
}

obs = summary(fit)$coefficients[3,1];
pvalue = (sum(abs(obs) <= out) + sum(-abs(obs)>=out)) / B;
pvalue

pdf("food_AB.pdf")
par(mar=c(4,4,3,1));
dev.new()
hist(out, xlab = expression(beta[compB]),
     main = "Distribution under Null hypothesis", freq = F);
obs = summary(fit)$coefficients[3,1];
text(obs, 0.39, expression(paste("obs ", beta[compB]),sep=""));
arrows(obs, 0.38, obs, 0, length = .125);
text(2.5, .3, paste("p-value= ", pvalue ,sep=""));
dev.off()

```

CI 95
```{r}
B   = 10000;
out = NULL;

for(i in 1:B){
  
  b     = sample(1:n, n, replace = TRUE);
  
  f1    = relevel(f[b], "A"); # A as baseline
  bfit  = lm(y[b] ~ x[b] + f1);
  
  out   = c(out, summary(bfit)$coefficients[3,1]);
  
}

round(quantile(out, prob = c(0.025, 0.975)), 3); # bootstrap CI
dev.new()
hist(out, xlab = "Difference in average");
text(4, 1500, paste("p-value= ", pvalue ,sep=""));
obs = summary(fit)$coefficients[3,1];
abline(v = obs, lty = 2); 
```

95ci
```{r}
y <- read.csv("~/Downloads/cavendish.txt", sep="")
x <- y$Density;
n = length(x);
xbar = mean(x);

pdf("cave.pdf")
par(mar=c(4,4,3,1))
dev.new()
hist(x, freq=F, main = "The density of the earth",
     xlab = "X");

mu_prior = 0;
sigma_prior = 1;
(mu_prior/sigma_prior)^(-1)

# Posterior parameters
mu_post = (n*xbar)/((n/xbar^2)+(1/sigma_prior^2));
sigma_post = ((n/xbar^2)+(1/sigma_prior^2))^-1/2;
(mu_post/sigma_post)^(-1)

# credible interval
round(qnorm(c(0.025, 0.975), mean=mu_post, sd=sigma_post),4);

```
Gibbs
```{r}
gibbs = function(n, mu1, mu2, s1, s2, rho, x0){
  
  x1_0 = x0[1];
  x2_0 = x0[2];

  out = NULL;
  
  for(i in 1:n){
  
    x1_0 = rnorm(1, mean = mu1 + rho * s1 * (x2_0 - mu2) / s2, 
               sd = sqrt((1-rho^2) * s1^2));
  
    x2_0 = rnorm(1, mean = mu2 + rho * s2 * (x1_0 - mu1) / s1, 
               sd = sqrt((1-rho^2) * s2^2));
    
    out = rbind(out, c(x1_0, x2_0));
  
  }
  
  return(out);
  
}  
# Specifications
n     = 29; # sample size
mu    = c(5.4,5);
rho   = 0.0;
s1    = 0.22;
s2    = 0.12;

set.seed(1)
R1 = gibbs(n = 29, mu1 = mu[1], mu2 = mu[2], s1 = s1, s2 = s2, 
           rho = rho, x0  = c(1,1));

pdf("lab2_case1_gibbs.pdf", width = 14, height = 3.5)
layout(matrix(c(1,3,4,5,2,3,4,5), 2, 4, byrow = TRUE))
par(mar= c(4,4,2,1))
dev.new()
plot(R1[,1], type = "l", xlab = "", ylab = "");
mtext("Iteration", side = 1, line = 2.5);
mtext(expression(X[1]), side = 2, line = 2.5);

dev.new()
plot(R1[,2], type = "l", xlab = "", ylab = "");
mtext("Iteration", side = 1, line = 2.5);
mtext(expression(X[1]), side = 2, line = 2.5);

dev.new()
plot(R1[,1], R1[,2], main = "", xlab = "", ylab = "");
mtext(expression(X[1]), side = 1, line = 2.5);
mtext(expression(X[2]), side = 2, line = 2.5);

dev.new()
hist(R1[,1], freq = FALSE, xlab ="", main = ""); curve(dnorm(x, mean=mu[1], sd =s1), add = TRUE);
mtext(expression(X[1]), side = 1, line = 2.5);

dev.new()
hist(R1[,2], freq = FALSE, xlab = "", main = ""); curve(dnorm(x, mean=mu[2], sd =s2), add = TRUE)
mtext(expression(X[2]), side = 1, line = 2.5);
dev.off()

coda::effectiveSize(R1[,1])
coda::effectiveSize(R1[,2])
```



Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

